Many claims of group polarization are plausibly false due to inappropriate statistics

### 2023-12-15 GroupPolarizationStatmod/paper/ms.tex
calculating cohen's d for, parallelized metric model

\subsubsection{$t$-tests of generated simple-consensus data}

@@

We generated these datasets by...

\subsection{Bayesian ordered-probit models reliably identify simple consensus}

\mt{Is this necessary or can we just reference Liddell \& Kruschke 2018 who show
that ordered-probit models accurately identify latent parameters when normal-distribution
models do not?}

@@

\subsection{Do $t$-tests accurately detect simple consensus?}

@@

\subsection{Do Bayesian ordered-probit models accurately detect simple consensus?}

@@

>>>>

\subsubsection{Metric model inference of Cohen's $d$ for simulated simple-consensus data}

@@

We generated these simulated data using the latent mean, pre-deliberation 
standard deviation, and post-deliberation standard deviations as parameters of
normal distributions of pre- and post-deliberation opinions.

\subsection{Bayesian ordered-probit models inference of Cohen's $d$ for simulated
simple-consensus data}

Non-metric ordered probit models, which account for the data collection 
process, theoretically should be better able to correctly
distinguish simple consensus compared to metric models. Therefore, we also fit
the following ordered probit model to simulated group polarization data.

@@

\subsection{Metric linear models fail to identify simple consensus}

@@

\subsection{Ordered-probit models also fail?}

@@

\subsection{More data enables ordered probit models, but not metric models, to reliably
  identify simple consensus}
